Hydras \& Co.

### 2022-04-17 doc/gaia-chapter.tex
minor corrections
update gaia-chapter

\inputsnippets{T1Bridge/E0Defb}
\inputsnippets{T1Bridge/E0plusMultDef}
\inputsnippets{GCanon/E0CanonDef, GCanon/E0CanonLt}

@@

\inputsnippets{GHydra/mDef}.

\inputsnippets{GHydra/mVariant, GHydra/Termination}.

@@

Finally, we relate the lenght of standard-battles with the $L_\alpha$ fast growing functions.

>>>>

\inputsnippets{T1Bridge/E0Defb}
\inputsnippets{T1Bridge/E0plusMultDef}

Canonical sequences are lifted to type \texttt{E0} in
\href{../theories/html/gaia_hydras.GCanon.html}{gaia\_hydras.GCanon}.

\inputsnippets{GCanon/E0CanonDef}
\inputsnippets{GCanon/E0CanonLt}

@@

\inputsnippets{GHydra/mDef}

\inputsnippets{GHydra/mVariant, GHydra/Termination}

\subsection{Impossibility Theorems}
\label{sect:impossibility-gaia-version}
The theorems described in Sect.~\vref{sect:impossibility-free}
and~\vref{sec:standard-battles-cases} are adapted to \gaia's world.

\inputsnippets{GHydra/impossibilityThms}

@@

Finally, we relate the length of standard-battles with the $L_\alpha$ fast growing functions.
